% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{superTLS: A Diverse and Redundant Secure Communication Channel for Privacy in Cloud}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Andr\'e Joaquim\\
       \affaddr{INESC-ID, Instituto Superior T\'ecnico, Universidade de Lisboa}\\
       \affaddr{R. Alves Redol 9, 1000-029}\\
       \affaddr{Lisbon, Portugal}\\
% 2nd. author
\alignauthor
Miguel L. Pardal\\
       \affaddr{INESC-ID, Instituto Superior T\'ecnico, Universidade de Lisboa}\\
       \affaddr{R. Alves Redol 9, 1000-029}\\
       \affaddr{Lisbon, Portugal}\\
% 3rd. author
\alignauthor
Miguel Correia\\
       \affaddr{INESC-ID, Instituto Superior T\'ecnico, Universidade de Lisboa}\\
       \affaddr{R. Alves Redol 9, 1000-029}\\
       \affaddr{Lisbon, Portugal}\\
       %
       \end{tabular}
       \begin{tabular}{c}
       \email{\{andre.joaquim, miguel.pardal, miguel.p.correia\}@tecnico.ulisboa.pt}  
}
% use '\and' if you need 'another row' of author names
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{03 May 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
We present superTLS, a diverse and redundant vulnerability-tolerant secure communication channel for privacy in cloud.
There have always been concerns about the strength of some of encryption mechanisms used in SSL/TLS channels and some of them were regarded as insecure at some point in time.
superTLS is our solution to mitigate the problem of secure communication channels being vulnerable to attacks due to unexpected vulnerabilities in its encryption mechanisms. It is based on diversity and redundancy of cryptographic mechanisms and certificates to provide a secure communication channel even when one or more mechanisms are regarded vulnerable.
superTLS relies on a combination of $k$ mechanisms/cipher suites, with $k$ being the diversity factor and $k > 1$.
Even when $k - 1$ mechanisms are regarded as insecure or considered vulnerable, superTLS relies on the remaining secure, diverse and redundant mechanism to maintain the channel secure.
We evaluated our channel by comparing it to a normal TLS channel and TLS-over-TLS.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003039.10003051</concept_id>
<concept_desc>Networks~Application layer protocols</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003083.10003014</concept_id>
<concept_desc>Networks~Network security</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010575.10010755</concept_id>
<concept_desc>Computer systems organization~Redundancy</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002978.10003014.10003015</concept_id>
<concept_desc>Security and privacy~Security protocols</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002978.10002979.10002982</concept_id>
<concept_desc>Security and privacy~Symmetric cryptography and hash functions</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Networks~Application layer protocols}
\ccsdesc[300]{Networks~Network security}
\ccsdesc[500]{Computer systems organization~Redundancy}
\ccsdesc[300]{Security and privacy~Security protocols}
\ccsdesc[100]{Security and privacy~Symmetric cryptography and hash functions}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Secure communication channels; Diversity; Redundancy; TLS; Vulnerability-Tolerance}

\section{Introduction}

\textit{Secure communication channels} are mechanisms that allow two entities to exchange messages or information securely in the Internet.
A secure communication channel has three properties: \textit{authenticity}, \textit{confidentiality}, and \textit{integrity}. Regarding authenticity, in an authentic channel, the messages can not be tampered. Regarding confidentiality, in a confidential channel, only the original receiver of a message is able to read that message. Regarding integrity, no one can impersonate another. The information regarding the original sender of a message can not be changed.
Several secure communication channels exist nowadays, such as TLS, IPsec or SSH. Each of these examples is used for a different purpose, but with the same finality of securing the communication.

\textbf{Transport Layer Security (TLS)} is a secure communication channel widely used. Originally called Secure Sockets Layer (SSL), its first released version was SSL 2.0, released in 1995. SSL 3.0 was released in 1996, bringing improvements to its predecessor such as allowing forward secrecy and supporting SHA-1.
Defined in 1999, TLS did not introduce major changes. Although, the changes introduced were enough to make TLS 1.0 incompatible with SSL 3.0. In order to grant compatibility, a TLS 1.0 connection can be downgraded to SSL 3.0, which brought security issues. TLS 1.1 and TLS 1.2 are upgrades which brought some improvements such as mitigating CBC (cipher block chaining) attacks and supporting more block cipher modes of operation to use with AES.
TLS is divided in two sub-protocols, Handshake and Record, constituted by several mechanisms each.
The Handshake protocol is used to establish or re-establish a communication between a server and client. The Record protocol is used to process the sent and received messages.

\textbf{Internet Protocol Security (IPsec)} is an Internet layer protocol that protects the communication at a lower level than SSL/TLS, which operates at the Application layer \cite{IPsec}.

\textbf{Secure Shell (SSH)} is an Application layer protocol, such as SSL/TLS. SSH is a protocol used for secure remote login and other secure network services over an insecure network \cite{SSH}.

A secure communication channel becomes insecure when a vulnerability is discovered. Vulnerabilities may concern the protocol's specification, cryptographic mechanisms used by the protocol or specific implementations of the protocol. Many vulnerabilities have been discovered in SSL/TLS originating new versions of the protocol with renewed security aspects such as deprecating cryptographic mechanisms or enforcing security measures.
Concrete implementations of SSL/TLS have been also considered vulnerable by having implementation details causing a breach of security and affecting devices worldwide.

\begin{itemize}
	\item {Description}
\end{itemize}

superTLS is a secure communication channel tolerant to vulnerabilities which does not rely on only one cryptographic mechanism. It is our belief that, in order to solve the problem, \textit{diversity} and \textit{redundancy} are helpful and can help mitigate the number of vulnerabilities.
Diversity and redundancy consist in using two or more different mechanisms with the same objective. For example, MD5 and SHA-3 are both hash functions used to generate digests. In a real case, where MD5 has become insecure, i.e., it is proved to have collisions, our diverse secure communication channel has other mechanism, SHA-3, to keep the communication secure. Using diversity and redundancy, when a mechanism is targeted by an attack, another mechanism is able to maintain the security and availability of the communication.

\begin{itemize}
	\item The contributions of this paper are: x,y,z
\end{itemize}

\begin{itemize}
	\item The rest of the paper is organized as followed: z,y,x
\end{itemize}

The rest of the document is organized in the following way: Section 3 presents the related work. Section 4 presents the architecture of the proposed solution. Section 5 presents how the solution is going to be evaluated. Section 6 presents the scheduling of the future work. Section 7 presents some conclusions.


\section{Related Work}

What are the current issues/vulnerabilities in the existing systems/mechanisms? 

\begin{itemize}
	\item{Brief TLS}
	\item{Mechanisms vulnerabilities}
	\item{Brief combining mechanisms OR brief diversity}
\end{itemize}

\section{SuperTLS/Architecture}

\begin{itemize}
\item Images updated from the thesis' project
\item Explain second cipher suite [X-Factor] audition and selection
\end{itemize}

\section{Experimental evaluation}

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}
%This section is optional; it is a location for you
%to acknowledge grants, funding, editing assistance and
%what have you.  In the present case, for example, the
%authors would like to thank Gerald Murray of ACM for
%his help in codifying this \textit{Author's Guide}
%and the \textbf{.cls} and \textbf{.tex} files that it describes.

\section{Future Work}

\begin{itemize}
\item Usar duas libraries e usar funções duma e doutra
\end{itemize}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\section{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The sig-alternate.cls file itself is chock-full of succinct
%and helpful comments.  If you consider yourself a moderately
%experienced to expert user of \LaTeX, you may find reading
%it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}
